---
title: "p8105_hw1_td2809"
author: "Chris Deng"
date: "2023-09-20"
output: html_document
---

```{r}
library(moderndive)
data("early_january_weather")
early_january_weather
```
The description of the dataset is:
```{r}
str(early_january_weather)
names(early_january_weather)
ncol(early_january_weather)
nrow(early_january_weather)
```
the mean temperature is
```{r}
 mean(early_january_weather$temp)
```

```{r}
library(tidyverse)
 p=ggplot(data=early_january_weather, aes(x=time_hour,y=temp,color=humid))
 p+geom_point()
```
The horizontal axis represents time, the vertical axis represents temperature, the color depth of the dots represents humidity, and the lighter the color, the higher the humidity.

```{r}
df=data.frame(x=rnorm(10),y=c(1,-2,3,4,-5,-6,7,-8,9,10)>0,z = c('1','2','3','4','5','6','7','8','9','10'),a=gl(3,3,length=10))
df
```


We can take the mean of x:
```{r}
mean_x=pull(df,x)
mean(mean_x)
```
We can take the mean of y:
```{r}
mean_y=pull(df,y)
mean(mean_y)
```

We can't take the mean of z:
```{r}
mean_z=pull(df,z)
mean(mean_z)
```
We can't take the mean of a:
```{r}
mean_a=pull(df,a)
mean(mean_a)
```
The as.numeric() function in R is used to convert a character vector,a logical vector and a factor vector into a numeric vector. Now we can take the mean of y, z and a.
```{r}
y1=as.numeric(mean_y)
z1=as.numeric(mean_z)
a1=as.numeric(mean_a)
```